### 2014-06-03 ACL2014/discussion.tex

\section{Discussion and Conclusion}
\label{sec:discuss}
In this section, we highlight several applications that take significant advantage of the approximate \dflipb algorithm presented in this paper.
One of the interesting applications of the near-neighbor finding is to understand specific intents behind the user query. 
Given a user's query, Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
to the user as the part of the search engine result page. 
Such direct display results are expected to reduce the number of unnecessary clicks by providing the user with the appropriate content early on. 
However, when the query "f today closing price" is issued to search engines, the three major search engines 
fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
By employing an algorithm similar to \dflipb, we can build a synonym database, 
which will help trigger the same direct display among related queries.

Yet another application is removing duplicated instances in a result set. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences 
would be distracted from ``duplicated results.'' 
That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
to find ``duplicated query terms'' efficiently. As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.  The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

We first described the existing ``vanilla'' \lsh algorithm. It is the first paper according to 
best of our knowledge that applies this algorithm to NLP applications. 
Next, we poposed four novel variants of vanilla \lsh. Two of our variants achieve 
significantly better recall than the vanilla LSH by using the same number of hash tables. 
We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.

>>>>

\section{Discussion}
\label{sec:discuss}
In this section, we highlight several applications that can take significant advantage of the approximate \dflipb algorithm presented in this paper.
One of the interesting applications of the near-neighbor finding is to understand specific intents behind the user query. 
Given a user's query, Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
to the user as the part of the search engine result page. 
Such direct display results are expected to reduce the number of unnecessary clicks by providing the user with the appropriate content early on. 
However, when the query "f today closing price" is issued to search engines, the three major search engines 
fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
By employing an algorithm similar to \dflipb, we can build a synonym database, 
which will help trigger the same direct display among related queries.

Yet another application is removing duplicated instances in a set of suggested results. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries
from the set so that the user is not distracted by duplicated results. Given a set of
we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
in order to find the ``duplicated query terms'' efficiently. 
As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity 
(relatively easier problem) than ``relatedness'', 
we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples. 
The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples-- ``trumbull weather ct'' and ``weather in trumbull ct''.

\section{Conclusion}
\label{sec:conclusion}
To the best of our knowledge, this is the first paper that applies
the vanilla \lsh algorithm of Andoni et al. to the NLP domain. 
We also proposed four novel variants of \lsh that are aimed to reduce the number 
of hash tables used. Two of our variants achieve 
significantly better recall than the vanilla LSH by using the same number of hash tables. 
We also present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial 
large-scale query logs (consisting of hundreds of millions of queries) in sublinear time.

### 2014-06-03 ACL2014/relatedwork.tex

\section{Related Work}
Locality sensitive hashing is a very well studied algorithmic tool, that has found practical uses too. 
In processing large text corpora, however, LSH algorithms have been less used, primarily because of their
still significant memory requirements. Recent work by~\cite{zadeh2013dimension} developed a modification of LSH algorithm, for 
the Jaccard distance metric, that scales to very large text corpora by virtue of being implemented on a map-reduce, 
and by using clever sampling schemes in order to reduce the communication cost. Our work is for the cosine similarity metric, 
and uses bit flipping in a distributed manner to reduce the number of hash tables in LSH and hence the memory. 
Other innovations to LSH methods in the text corpora analysis domain include developing methods to compute
LSH signatures in an online manner~\cite{van2010online}, and using reservoir sampling to compute the signatures~\cite{van2011efficient}.

>>>>

\section{Related Work}

There has been many papers in last decade that have focused on 
approximate, streaming, and randomized algorithms on many NLP problems. 
Prior work on \lsh for noun clustering \cite{ravichandran05} applied 
original version of \lsh based on \plebf (PLEB) \cite{Indyk98STOC,Charikar02STOC}. 
The disadvantage of original \lsh algorithm is that it involves generating large number of permutations ($L=1000$, 
generating permutation is similar to generating more tables)
and sorting bit vectors of large width ($K=3000$). 
To address that issue, Goyal et al. \cite{goyal12Flag} proposed a new variant of PLEB that
is faster than the original \lsh algorithm but that still requires large number of permutations 
($L=1000$). In addition, their work can be seen as an implementing a special case of Andoni and Indyk's \lsh algorithm.

The next major difference between our research and existing work is that the 
existing work deals with approximating cosine similarity by Hamming distance  
\cite{ravichandran05,vandurme-lall:2010:Short,vandurme-lall:2011:Short,goyal12Flag}. 
In that problem setting, the goal is to minimize both false positives and negatives. 
In our work, we focus on minimizing false negatives with zero tolerance for false positives.

\cite{zadeh2013dimension} developed a distributed version of the LSH algorithm, for 
the Jaccard distance metric, that scales to very large text corpora by virtue of being implemented on a map-reduce, 
and by using clever sampling schemes in order to reduce the communication cost. Our work is for the cosine similarity metric, 
and uses bit flipping in a distributed manner to reduce the number of hash tables in LSH and hence the memory.
